\documentclass{article}
\usepackage{amsmath} % for mathematical symbols
\usepackage{graphicx} % for including images
\usepackage{listings}
\usepackage{hyperref}

\usepackage[a4paper, total={6.5in, 10in}]{geometry}

\begin{document}
	
	\title{\vspace{-1.5cm}Ex03 \\ Answers \& Manual}
	\author{Paul Tr\"oger, Fynn Gohlke, Tom Rodewald, Jan B\"uchele}
	
	\maketitle
	
	\section{Answers}
		\subsection{Shamir secret sharing}
            We assume that all parties share the same known x evaluation points for shamir secret sharing. In our code we draw these from a fixed seed with np.random.choice. This is necessary for adding shares together.
		\subsection{Ben-Or, Goldwasser, and Wigderson (BGW) Protocol}
            \textbf{Assumption}:\\
            We assume that all parties share the same known x evaluation points for shamir secret sharing. In our code we draw these from a fixed seed with np.random.choice. Each party is responsible for evaluation point $x_p$ where $p$ is the party id.\\\\
            \textbf{Protocol}:
            \begin{enumerate}
                \item We generate shamir secrets for $a, b$ with $t, n$ getting $n$ shares per secret.
                \item We initialize n parties so that each party gets \textbf{one share per secret}.
                \item We start round 1 by handing out shares:
                    \begin{enumerate}
                        \item Each party multiplies it's secret shares y values, increasing the polynomials degree to 2t.
                        \item Each party generates a new shamir secret where $q(x_p) = p_\alpha(x_p) * p_\beta(x_p)$.
                        \item Each party sends out $n$ shares for $q(x_p)$ to the $n$ parties.
                    \end{enumerate}
                \item Each party now holds $n$ shares for their assigned evaluation point $x_p$.
                \item We start round 2:
                    \begin{enumerate}
                        \item Each party calculates Lagrange coefficients as described in \ref{lagrange}.
                        \item Each party calculates $q(0) = \sum_{i=1}^{2t+1} \lambda_iq(i)$ as described in "A Pragmatic Introduction to Secure Multi-Party Computation" for each party and store it in the output variable.
                    \end{enumerate}
                \item We retrieve the output from all parties with get\_view() and reconstruct the value.
            \end{enumerate}
            \subsubsection{Lagrange Coefficients}\label{lagrange}
                The Lagrange Coefficients are defined as 
                \begin{equation*}
                    L_k(x) = \prod_{i=0,i\not=k}^n \frac{(x-x_i)}{(x_k-x_i)}
                \end{equation*}
                with properties $L_k(x_k) = 1$ and $L_k(x_j) = 0$ where $x_j \not= x_k$.

    \newpage
	\section{Manual}
		\subsection{Running the code}
		All source code is self contained within a singular file called "e3.py".\\
		Running the application can be achieved using \textit{python3 e3.py}.\\
		This runs all the tasks and their respective outputs, Listing \ref{lst:python-output} shows the output of running the application normally.\\
		There are also python tests defined within the application. These can be run using \textit{pytest -v e3.py}.\\
		The flag "-v" is not mandatory, but improves clarity on what actually happened.\\
		Running the tests with the aforementioned command results in an output similar to Listing \ref{lst:pytest-output}.
		
		\subsection{Test Cases}
	
		\subsubsection{Task 1 Tests}
		
		\subsubsection{Task 2 Tests}
        We wrote two tests for \lstinline{run_bgw(t, n, a, b)} which also tests BGW class.\\
        In test one \lstinline{test_run_bgw_large_t()} we check that the assert inside \lstinline{round1()} throws an exception if $2t+1 <= n$.\\
        In test two \lstinline{test_run_bgw_correctness()} we test different configurations and their output.\\
        We test \lstinline{get_lagrange_coeffs(x_values)} with a two point and three point example. We can calculate the result per hand and verify if our function outputs correct Lagrange coefficients. See \ref{lagrange} for Lagrange equation.
		
	
		\section{Appendix}
			\subsection{Python-output}\label{lst:python-output}
				%\lstinputlisting{python-output}
			\subsection{Pytest-output}
				%lstinputlisting{pytest-output}\label{lst:pytest-output}
\end{document}
